---
title: "network2activity"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{network2activity}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(network2activity)
```

# Introduction

The package includes some functions to get a Contextual Activity Score (CAS) of
ADAR proteins. This can be done with just a normalized count expression matrix
by using the already available signatures, specific for different biological
contexts. Otherwise, if the reconstructed regulatory network of your dataset is
available, you can compute your own regulon and use it to infer the protein
activity.

## Infer ADAR activity with the dataset-specific regulon

```{r}
# Load the example data
data(example_network)
data(example_matrix)
data(example_genes)

# Infer ADAR activity
res <- yourSignature(example_matrix, example_network, example_genes, 
                     file_name = "interactors_scores")
```

## Compute ADAR activity with the cancer-related signature

```{r}
# Load the regulon
data(tumoral_regulon)

# Load the example expression matrix
data(example_matrix)

# Compute ADAR activity
res <- tumoralSignature(example_matrix, object = "bulk")
```

## Compute ADAR activity with the neuronal signature

```{r}
# Load the regulon
data(neuronal_regulon)

# Load the example expression matrix
data(example_matrix)

# Compute ADAR activity
res <- neuronalSignature(example_matrix, object = "bulk")
```

## Compute ADAR activity with the mouse-specific neuronal signature

```{r}
# Load the regulon
data(mouse_neuronal_regulon)

# Load the example expression matrix
data(example_matrix_Mm)

# Compute ADAR activity
res <- neuronalMmSignature(example_matrix_Mm, object = "bulk")
```

