---
title: "network2activity"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{network2activity}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(network2activity)
```

# Introduction

The package comprises some functions which, from a regulatory network and a gene 
expression matrix obtained by RNA-Seq data and a list of regulator genes, 
allows to infer the protein activity employing VIPER.

## Get the data frame from the network obtained by the network reconstruction with ARACNe

```{r}
data(network)
net_df <- getDf(network)
```

## The function filters the data frame obtained by the network to consider only the regulators of the gene of interest and, for each regulator, it gets a list of their interactors and the corresponding scores

```{r}
data(network_df)
data(regulators_list)
interactors <- getInteractorsList(network_df, regulators_list)
```

## Get the adjacency matrix file as requested by VIPER

```{r}
interactors_adj <- writeAdjFile(interactors, file_name = "interactors")
```

## Infer ADAR activity with the dataset-specific signature

```{r}
inferenceWithYourSignature(interactors_adj, vsd_matrix)
```

## Infer ADAR activity with the A549 cells signature

```{r}
data(regul_A549_cells)
data(vsd_matrix)
inferenceWithA549Signature(vsd_matrix)
```

## Infer ADAR activity with the neurons-specific signature

```{r}
data(regul_hESC_neurons)
inferenceWithNeuronsSignature(vsd_matrix)
```

## Infer ADAR activity with the interferon-specific signature

```{r}
data(regul_interferon_specific)
inferenceWithInterferonSignature(vsd_matrix)
```

